%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 2.0 (6/7/2019)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{article} % Default document font size

\input{structure.tex} % Include the file specifying the document structure and styling

% Set PDF meta-information
\hypersetup{
	pdftitle={Michael Sullivan - Curriculum vitae},
	pdfauthor={Michael Sullivan}
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION
%----------------------------------------------------------------------------------------
 \begin{flushright}
   \scriptsize
	Last updated: \today
   \normalsize
\end{flushright}
{\LARGE\bfseries Michael Rolland Sullivan} % Name
\bigskip\bigskip\medskip % Whitespace

\medskip % Whitespace

Email: \href{mailto:m.r.sullivan@yale.edu}{m.r.sullivan@aya.yale.edu}\\ 
Website: \href{https://sites.google.com/view/michaelrsullivan/home}{https://sites.google.com/view/michaelrsullivan}\\ 

%\section*{Fields of concentration}
%
%Industrial organization; Economics of digitization; Applied econometrics 

\section*{Academic appointments}

\years{2024--} Assistant professor, Western University (University of Western Ontario) 

\years{2023} Post-doctoral fellow, Harvard Business School


\section*{Education}

\years{2023}\textsc{Ph.D.} in Economics, Yale University  

\hspace{1cm} \small Committee: Katja Seim (chair), Philip Haile, Steven Berry \normalsize

\years{2020}\textsc{M.Phil.} in Economics, Yale University 

\years{2018}\textsc{M.A.} in Economics, Yale University 

\years{2016}\textsc{B.Sc.} in Pure Mathematics and Economics, Memorial University of Newfoundland

\section*{Working papers}

Price Controls in a Multi-Sided Market. 2024. 
\begin{itemize}
	\item \textit{Revision requested at the Journal of Political Economy.}
\end{itemize}

\medskip

Sources of Limited Consideration and Market Power in E-commerce. 2024.
\begin{itemize}
	\item \textit{Conditionally accepted at American Economic Journal: Microeconomics.}
\end{itemize}

\medskip

Cross-Channel Competition and Complementarities in US Retail
(with Hiroki Saruya). 2023.

\medskip

 
Demand with Network Externalities: 
Identification and an Application to the Dating Websites Industry. 2022.

\section*{Work in progress}

Approaches to Encouraging Health Exchange Participation 
(with Soheil Ghili, Igal Hendel, and Michael Whinston)


\section*{Publications}

Market Design for Personal Data
(with Dirk Bergemann, Jacques Cr\'{e}mer, David Dinielli, 
Carl-Christian Groh, Paul Heidhues, Maximillian Schaefer, 
Monika Schnitzer, Katja Seim, and Fiona M.\ Scott Morton).
2023. \textit{Yale Journal on Regulation.}




\section*{Conference and Seminar Presentations}

\years{Scheduled} Queen's University, the University of Waterloo,
the University of British Columbia (Sauder School of Business),
NBER ``Digital Platforms: Competition and Regulation'' Workshop

\years{2024} Allied Social Science Associations (ASSA) Annual Meeting
	(Econometric Society session, ``Pricing and Demand with Digital/Online Markets'');
	International Industrial Organization Conference;
	2024 Canadian Economic Association Annual Meetings;
		the Economics of Platforms and Recommender Systems Workshop (Telecom Paris)
	
\years{2023} Bank of Canada; University of Western Ontario;
	McGill University; Columbia Business School --- Decision, Risk, and Operations;
	Northwestern University; UNC Chapel Hill; University of Toronto Rotman School
	of Management; Federal Reserve Board; Toulouse School of Economics;
	NBER Summer Institute (Industrial Organization and Digital Economics and Artificial
	Intelligence sections); University of Michigan (IO Seminar);
	Stanford University (IOPLUS seminar); Bank of Canada Payments, Multi-Sided Platforms, and Payments
	Workshop (as discussant); 
	Harvard Business School (D${}^3$ Seminar); 
	National Association for Business Economics TEC Conference;
	The Ohio State University (Applied Microeconomics Seminar)


\years{2022} 5th Doctoral Workshop on the Economics of Digitization, Ifo Institute; 
	Young Economist Symposium (at Yale University); Amazon Core AI


\years{2021} Young Economist Symposium (at Princeton University)

\section*{Awards}

\years{2023} George Trimis Prize for distinguished dissertations in economics (Yale University)

\years{2016} Governor General's Medal for best academic performance in university's graduating class
	(Memorial University of Newfoundland)

\section*{Grants}

\years{2024} Faculty of Social Science Samuel Clark Internal Research Grant (Western University), \$5k CAD

\years{2021}  Doctoral Fellowship, Social Sciences and Humanities Research Council (SSHRC), \$20k CAD


\section*{Referee service}

\textit{RAND Journal of Economics} ($\times$ 4), \textit{American Economic Review},
\textit{American Economic Journal: Microeconomics} ($\times$ 2),
 \textit{Journal of Political Economy Microeconomics},
\textit{Journal of International Economics}, \textit{the Economic Journal},
\textit{Information Systems Research}


%
%\section*{Experience}
%
%\years{2021-2022} Research assistant for Profs Fiona Scott Morton and 
%	Dirk Bergemann (Yale) \\
%
%\years{2020} Research assistant for Prof Yuichi Kitamura (Yale) \\
%\years{2018--2020} Research assistant for Profs Soheil Ghili (Yale SOM), Igal Hendal (Northwestern), and Michael Whinston (MIT) \\
%\years{2016--2017}  Research assistant for Profs Matthew Gentzkow (Stanford) and Jesse Shapiro (Brown) \\
%\years{2015} Research assistant, Bank of Canada \\


\section*{Citizenship}

Canada

%\section*{Teaching}
%
%\years{Fall 2020} Econometrics I (graduate, Prof Donald Andrews) \\
%\years{Spring 2020} Econometrics III (graduate, Prof Yuichi Kitamura) \\
%\years{Fall 2019} Introduction to probability and statistics (undergraduate, Prof Timothy Armstrong)
%


%------------------------------------------------

\vfill % Whitespace before final footer



\end{document}
